---
output:
  pdf_document: default
  fig_caption: false
params:
  data: !r as.character("")
  variance.data: !r as.character("")
  variable: !r as.character("")
  exposure: !r as.character("")
  model: !r as.character("")
  observed: !r as.character("")
  clm.count: !r as.character("")
header-includes:
  - \usepackage[T1]{fontenc}
  - \usepackage{lmodern}
  - \usepackage{hyperref}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\pagenumbering{gobble}

# `r gsub('_',' ',params$variable)`

Date Produced: `r format(Sys.time(), '%d %B, %Y')`

```{r data, echo=FALSE, message=FALSE, warning=FALSE}
X<-TDTools::Plot.Data(DATA = params$data,
                      VARIANCE.DATA = params$data,
                      NAMES = list(MODELS    = params$model,
                                   OBSERVED  = params$observed,
                                   CLM.COUNT = params$clm.count,
                                   EXPOSURE  = params$exposure,
                                   VARIABLE  = params$variable),
                      MODE = "ALL",
                      EVAL.VARIANCE = T,
                      SPLIT.VARIANCE = F,
                      N.BKTS = 20)

```


## Predicted vs. Observed Chart

![](`r TDTools::PvO.Chart(X, AS.PDF = T)`)
\begin{center}
\begin{Form}
\TextField[name=comment1, multiline=true, align=0, width=400pt, height=6\baselineskip]{ }
\end{Form}
\end{center}

## Discrepency Chart

![](`r TDTools::Discrepency.Chart(X, AS.PDF = T)`)
\begin{center}
\begin{Form}
\TextField[name=comment2, multiline=true, align=0, width=400pt, height=6\baselineskip]{ }
\end{Form}
\end{center}


## Deviation Chart

![](`r TDTools::Deviation.Chart(X,DATA.ONLY=TRUE,AS.PDF = T)`)
\begin{center}
\begin{Form}
\TextField[name=comment3, multiline=true, align=0, width=400pt, height=6\baselineskip]{ }
\end{Form}
\end{center}






